% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Natalia Kapralova}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{Tel: +44 7899040617}
 \moveleft.5\hoffset\centerline{Email: natkapral@gmail.com}
 

\begin{resume}
 
\section{OBJECTIVE}  Software engineer who is experienced with a wide range of backend technologies. I am  specializing  primarily in Python/Django and PHP/Symfony2 and seek challenging position in an exciting, dynamic environment.
 
\section{TECHNICAL \\ SKILLS}
                \begin{itemize} \itemsep -2pt
                    \item Strong: Linux, Python/Django,  PHP/Symfony2, Twig, Solr, Mysql, Postgres, Git, Docker, Vagrant, Fabric 
                    \item Knowledgeable:AWS, Flask, Apache, Nginx, RabbitMQ, JavaScript, CSS, HTML, Bootstrap, Doctrine
                \end{itemize}

\section{EXPERIENCE} {\sl Software Engineer} \hfill Sept 2010 – Present time \\
                Tangent Labs, London , UK \\ \\
                Duties and Responsibilities:
                \begin{itemize} \itemsep -2pt
                    \item Develop new functionality and maintain existing e-commerce web applications using Python/Django or PHP/Symfony2 , Mysql or Postgres, Solr, RabbitMQ
                    \item Deploy applications using AWS, Docker, Fabric.
                    \item Implement requirements for new functionality, content and changes to required sites or applications as required by the business.
                    \item Ensure functionality developed is unit tested before system testing
                    \item Ensure that project progress is communicated effectively; projects are delivered to schedule and ensure that only authorized changes are delivered. 
                    \item Lead on technical design and analysis, report team progress and metrics of resource and time allocation and improvement. 
                \end{itemize}

                {\sl Web Developer} \hfill            Aug 2007 – Aug 2008 \\
                Northern Shipyards, St-Petersburg, Russia \\
                \begin{itemize} \itemsep -2pt
                    \item Developed and maintained the internal system for managing documents within the company.
                    \item Full stack developer using PHP, HTML, CSS, JavaScript
                \end{itemize}

                {\sl Web Developer} \hfill        Sep 2005 – June 2007 \\
                Plazma, St-Petersburg, Russia \\
                \begin{itemize} \itemsep -2pt
                    \item Developed web applications for small and medium businesses
                    \item  Full stack developer using PHP, HTML, CSS, JavaScript
                \end{itemize}
\section{SIDE  \\ PROJECTS}
                {\sl Multiligual e-commerce project: cloth store}
                \begin{itemize} \itemsep -2pt
                    \item Developed using PHP/Symfony2 and Sylius 
                    \item Implemented integration with a warehouse and payment system.
                    \item Used Solr for the search and AWS for storing media and hosting.
                \end{itemize}

\section{EDUCATION} {\sl MSc in Web Intelligence (Pass With Distinction)} \hfill Sep 2009 – Sep 2010 \\
                King's College London, UK \\
                \begin{itemize} \itemsep -2pt
                    \item Developed an application for Battleship Game using JSP 
                    \item Designed an algorithm for the two-dimensional strip packing problem, implemented it using PHP and provided comparison analysis with existing ones.
                \end{itemize}


                {\sl BSc Information Technology} \hfill Sep 2002 - June 2007 \\
                St. Petersburg State University, Russia \\
                \begin{itemize} \itemsep -2pt
                    \item Developed Content System Management using PHP, HTML, CSS, JavaScript 
                    \item Provided integration with Ozon services using REST APIs.
                \end{itemize} 


\end{resume}
\end{document}



